---
title: "Peer Assessment II"
output:
  html_document: 
    pandoc_args: [
      "--number-sections",
    ]
---

# Background

As a statistical consultant working for a real estate investment firm, your task is to develop a model to predict the selling price of a given home in Ames, Iowa. Your employer hopes to use this information to help assess whether the asking price of a house is higher or lower than the true value of the house. If the home is undervalued, it may be a good investment for the firm.

# Training Data and relevant packages

In order to better assess the quality of the model you will produce, the data have been randomly divided into three separate pieces: a training data set, a testing data set, and a validation data set. For now we will load the training data set, the others will be loaded and used later.

```{r load, message = FALSE}
load("ames_train.Rdata")
```

Use the code block below to load any necessary packages

```{r packages, message = FALSE}
library(statsr)
library(dplyr)
library(BAS)
library(MASS)
library(GGally)
library(ggplot2)
library(gridExtra)
```

## Part 1 - Exploratory Data Analysis (EDA)

When you first get your data, it's very tempting to immediately begin fitting models and assessing how they perform.  However, before you begin modeling, it's absolutely essential to explore the structure of the data and the relationships between the variables in the data set.

Do a detailed EDA of the ames_train data set, to learn about the structure of the data and the relationships between the variables in the data set (refer to Introduction to Probability and Data, Week 2, for a reminder about EDA if needed). Your EDA should involve creating and reviewing many plots/graphs and considering the patterns and relationships you see. 

After you have explored completely, submit the three graphs/plots that you found most informative during your EDA process, and briefly explain what you learned from each (why you found each informative).

* * *

```{r creategraphs}
# Check for missing values in the dataset

null_val <- colSums(is.na(ames_train))
null_val2 <- sort(null_val, decreasing = TRUE)[1:20]

barplot(null_val2 , main = "Blank or MIssing values", las = 2 )
```
The NA's in the dataset reflect unavailable assets for the individual features and not missing data. It is critical that we understand this distinction so that we can trust the fidelity of the data collection processes.

### Response Variable Distribution

It is important to verify that the models' assumptions will correspond to the actual features of the data as they will predict the interactions.

The data should be normally distributed to ensure a valid result Working with linear regression. We will now examine the price variable in the training set.

```{r priceVariable}
ames_train %>% 
    summarize(Q1 = quantile(price, 0.25), 
              MEAN = mean(price), 
              MEDIAN = median(price), 
              Q3 = quantile(price, 0.75), 
              IQR = IQR(price), 
              SD = sd(price))

p1 <- ggplot(ames_train) + 
        geom_histogram(aes(price, ..density..), fill = "red", alpha = 0.2)  +         
        geom_density(aes(price, ..density..), color = "magenta") 

p2 <- ggplot(ames_train) +   
      geom_histogram(aes(log(price), ..density..), fill = "green", alpha = 0.2)  +       
      geom_density(aes(log(price), ..density..), color = "blue")

grid.arrange(p1, p2, ncol =2)
```

The price variable shows an approximately normal distribution with a slight right skew.

A log transform of the variable shows improvement in the distribution.

Previous analysis of this dataset indicates that Overall Quality has a strong relationship with price.

```{r qual-price}
ggplot(ames_train, aes(factor(Overall.Qual),price)) +
  geom_boxplot() +
  geom_point(aes(color=factor(Overall.Qual)), position=position_dodge(width = 0.5))
```

The boxplots illustrate the distribution of the housing prices for each quality level. The higher the overall quality, the higher the mean price of the houses.

There is a larger spread as the overall quality of the houses increases. This means that other  variables contribute to prices as well. 

Greater outliers appear in bins 6 to 9. Something to note as we move forward with our analysis.

### Studying the relationship between Overall Area and Price

```{r area-price}
p1 <- ggplot(ames_train, aes(area, log(price))) +
       geom_point(color = "red", alpha = 0.2) + 
       geom_smooth(method=lm, se=TRUE) 

p2 <- ggplot(ames_train, aes(log(area), log(price))) +
       geom_point(color = "green", alpha = 0.2) +   
       geom_smooth(method = lm, se = TRUE)

grid.arrange(p1, p2, ncol=2)
```

Log transforming area produces a better result as with price. This affirms our analysis from previous exercises with this dataset.

* * *

## Part 2 - Development and assessment of an initial model, following a semi-guided process of analysis

### Section 2.1 An Initial Model
In building a model, it is often useful to start by creating a simple, intuitive initial model based on the results of the exploratory data analysis. (Note: The goal at this stage is **not** to identify the "best" possible model but rather to choose a reasonable and understandable starting point. Later you will expand and revise this model to create your final model.

Based on your EDA, select *at most* 10 predictor variables from “ames_train” and create a linear model for `price` (or a transformed version of price) using those variables. Provide the *R code* and the *summary output table* for your model, a *brief justification* for the variables you have chosen, and a *brief discussion* of the model results in context (focused on the variables that appear to be important predictors and how they relate to sales price).

* * *

The Adjusted R squared of the initial model is acceptable at 0.85 and the the p-value of the model's F-statistic indicates that the model as a whole is acceptable.

```{r fit_model}
model_lm = lm(log(price) ~ log(area) + 
                Overall.Qual + 
                Overall.Cond + 
                Kitchen.Qual + 
                Bsmt.Qual + 
                Exter.Qual + 
                Year.Built + 
                Garage.Area + 
                Lot.Area , 
              data = ames_train )

summary(model_lm)
anova(model_lm)
```

* * *

### Section 2.2 Model Selection

Now either using `BAS` another stepwise selection procedure choose the "best" model you can, using your initial model as your starting point. Try at least two different model selection methods and compare their results. Do they both arrive at the same model or do they disagree? What do you think this means?

* * *

We will employ two different model selection types based upon the initial model: 

1. Step AIC
2. BMA with BIC.

```{r model_select}
# step AIC
model_AIC <- stepAIC(model_lm, k = 2)

model_AIC$anova
coef(model_AIC)

# BMA
model_BIC = bas.lm(model_lm,
                    prior = "BIC",
                    modelprior = uniform(),
                    data = ames_train)

image(model_BIC, rotate = TRUE)
coef(model_BIC, estimator = "BMA")
```

* * *

### Section 2.3 Initial Model Residuals
One way to assess the performance of a model is to examine the model's residuals. In the space below, create a residual plot for your preferred model from above and use it to assess whether your model appears to fit the data well. Comment on any interesting structure in the residual plot (trend, outliers, etc.) and briefly discuss potential implications it may have for your model and inference / prediction you might produce.

* * *

We will select the BMA model as our preferred model and will conduct the residuals analysis.

```{r model_resid}
pred_price <- predict(model_BIC, ames_train, estimator = "BMA")

resid_price <- na.omit(data.frame(actualPrice = ames_train$price, 
                                  fittedPrice = exp(pred_price$fit))) %>% 
  mutate(PriceResidual = actualPrice - fittedPrice)

ggplot(data = resid_price, aes(x = fittedPrice, y = PriceResidual)) + 
  geom_point(col = 'magenta', alpha = 0.3) + 
  geom_smooth(method = "lm", se = TRUE) + 
  geom_hline(yintercept = 0, linetype = 'dashed', color = 'black')
```

* * *

### Section 2.4 Initial Model RMSE

You can calculate it directly based on the model output. Be specific about the units of your RMSE (depending on whether you transformed your response variable). The value you report will be more meaningful if it is in the original units (dollars).

* * *

The within-sample root-mean-squared error is in dollars

```{r model_rmse}
rmse <- sqrt(mean(resid_price$PriceResidual^2))
rmse
```

* * *

### Section 2.5 Overfitting 

The process of building a model generally involves starting with an initial model (as you have done above), identifying its shortcomings, and adapting the model accordingly. This process may be repeated several times until the model fits the data reasonably well. However, the model may do well on training data but perform poorly out-of-sample (meaning, on a dataset other than the original training data) because the model is overly-tuned to specifically fit the training data. This is called “overfitting.” To determine whether overfitting is occurring on a model, compare the performance of a model on both in-sample and out-of-sample data sets. To look at performance of your initial model on out-of-sample data, you will use the data set `ames_test`.

```{r loadtest, message = FALSE}
load("ames_test.Rdata")
```

Use your model from above to generate predictions for the housing prices in the test data set.  Are the predictions significantly more accurate (compared to the actual sales prices) for the training data than the test data?  Why or why not? Briefly explain how you determined that (what steps or processes did you use)?

* * *

The test RMSE is smaller than the training RMSE. The training set seems to be based on a large variety of houses, while the test set houses are more homogeniac.

```{r initmodel_test}

pred_test <- predict(model_BIC, ames_test,estimator = "BMA")
resid_test <- na.omit(ames_test$price - exp(pred_test$fit))
rmse_test <- sqrt(mean(resid_test^2))

```
```{r}
summary(pred_test)
summary(resid_test)
rmse_test
```

* * *

**Note to the learner:** If in real-life practice this out-of-sample analysis shows evidence that the training data fits your model a lot better than the test data, it is probably a good idea to go back and revise the model (usually by simplifying the model) to reduce this over fitting. For simplicity, we do not ask you to do this on the assignment, however.

## Part 3 Development of a Final Model

Now that you have developed an initial model to use as a baseline, create a final model with *at most* 20 variables to predict housing prices in Ames, IA, selecting from the full array of variables in the dataset and using any of the tools that we introduced in this specialization.  

Carefully document the process that you used to come up with your final model, so that you can answer the questions below.

### Section 3.1 Final Model

Provide the summary table for your model.

* * *

A BAS model with the following variables was selected:

* `log(price)`
* `log(area)`
* `Overall.Qual` 
* `Overall.Cond`
* `Kitchen.Qual`
* `Bsmt.Qual`
* `Exter.Qual`
* `Year.Built`
* `Garage.Area`
* `Lot.Area`

These features are based upon the previous analysis performed using BMA. The coefficients for this model  had a posterior inclusion probability of greater than 0.01.


```{r model_playground}
model_opt <- bas.lm(log(price) ~ log(area) + 
                      Overall.Qual + 
                      Overall.Cond + 
                      Kitchen.Qual + 
                      Bsmt.Qual + 
                      Exter.Qual + 
                      Year.Built + 
                      Garage.Area + 
                      Lot.Area, 
                      data = ames_train, 
                      prior = "BIC",
                      modelprior = uniform())

plot(model_opt, 4)
coefs <- coef(model_opt, estimator = "BMA")
pred_price <- predict(model_opt, ames_test, estimator = "BMA")
```

* * *

### Section 3.2 Transformation

Did you decide to transform any variables?  Why or why not? Explain in a few sentences.

* * *

Both the response variable (price) and the explanatory variable (area) were log transformed. This normalized the data and allowed for a linear model.

```{r model_assess}
```

* * *

### Section 3.3 Variable Interaction

Did you decide to include any variable interactions? Why or why not? Explain in a few sentences.

* * *

No variable interactions were included  based upon the explanatory variables choices.

```{r model_inter}
```

* * *

### Section 3.4 Variable Selection

What method did you use to select the variables you included? Why did you select the method you used? Explain in a few sentences.

* * *

The BAS package using Bayes Model Averaging (BMA) was used to manage variable selection. The BMA process reduces or eliminates the coefficients that have a low posterior probability of inclusion in the model. This allows more information to be preserved by not totally eliminating some variables, but also limits the effects of over fitting by reducing the magnitude of the coefficients for low posterior probability variables.


```{r model_select}
```

* * *

### Section 3.5 Model Testing

How did testing the model on out-of-sample data affect whether or how you changed your model? Explain in a few sentences.

* * *

The testing RMSE was lower than the training RMSE; eliminating  over fitting as a key concern for the model. 

Model performance was better for the testing set.

```{r model_testing}
```

* * *

## Part 4 Final Model Assessment

### Section 4.1 Final Model Residual

For your final model, create and briefly interpret an informative plot of the residuals.

* * *

The QQ plots also show positive results, with residuals distributed normally auto 2 standard deviations. The observed residuals have improved for the test set.

Heteroskedasticity has been reduced compared to the initial model.

```{r residualsFinalModel}
resid_price <- na.omit(data.frame(actualPrice = ames_test$price, fittedPrice = exp(pred_price$fit))) %>% 
    mutate(PriceResidual = actualPrice-fittedPrice)

ggplot(data = resid_price, aes(x = fittedPrice, y = PriceResidual)) + 
  geom_point(col = 'darkgreen', alpha = 0.2) + 
  geom_smooth(method = "lm", se = TRUE) + 
  geom_hline(yintercept = 0, linetype = 'dashed', color = 'black')

qqnorm(resid_price$PriceResidual, lty = 2)
qqline(resid_price$PriceResidual)


```


* * *

### Section 4.2 Final Model RMSE

For your final model, calculate and briefly comment on the RMSE.

* * *

The final model RMSE is significantly lower than previous iterations. This was helpful in determining the final model variable selections and modelling approach choices.

```{r rmse_final}
rmse_final = sqrt(mean(resid_price$PriceResidual^2))
rmse_final
```


* * *

### Section 4.3 Final Model Evaluation

What are some strengths and weaknesses of your model?

* * *

* The strength of the model is in the explanatory element as predictions are within ~$25k deviation from the actual prices.

* The weakness of the model is in inconsistency  for houses that have extremely positive price outliers. The model estimates more conservative prices.

* * *

### Section 4.4 Final Model Validation

Testing your final model on a separate, validation data set is a great way to determine how your model will perform in real-life practice. 

You will use the “ames_validation” dataset to do some additional assessment of your final model. Discuss your findings, be sure to mention:
* What is the RMSE of your final model when applied to the validation data?  
* How does this value compare to that of the training data and/or testing data?
* What percentage of the 95% predictive confidence (or credible) intervals contain the true price of the house in the validation data set?  
* From this result, does your final model properly reflect uncertainty?

```{r loadvalidation, message = FALSE}
load("ames_validation.Rdata")
```

* * *

The RMSE is lower in the validation set than both the training and test datasets. 

```{r model_validate}
price_valid <- predict(model_opt, ames_validation, estimator = "BMA")

resid_valid <- na.omit(ames_validation$price - exp(price_valid$fit))
rmse_valid <-  sqrt(mean(resid_valid^2))
rmse_valid
```

* * *

## Part 5 Conclusion

Provide a brief summary of your results, and a brief discussion of what you have learned about the data and your model. 

* * *

We can predict the housing prices for Ames, Iowa using linear regression within $25,000 based on features of the house through Bayes Model Averaging. Neighborhood, Overall quality, and Overall size of individual houses are strong predictors for estimating housing prices.

Linear regression models can overall consistently predict home prices for the majority of houses for this market.
However, positive outliers are being under-priced with this model.

Despite the models limitations it does fulfill its intended purpose; estimating average housing prices fairly accurately.

* * *
